Towards an open-source landscape for 3D CSEM modelling

### 2021-07-05 manuscript/Manuscript.tex
Final edits

\date{Received 2021 MMMM DD; in original form 2020 October 23}
\pagerange{\pageref{firstpage}--\pageref{lastpage}}
\volume{VVV}
\pubyear{202Y}

@@

%
\begin{table*}
\begin{minipage}{.9\linewidth}
  \centering
  \caption{Comparison of the four codes under consideration. Note that \emg3d is a solver on its own, while the other codes implement third-package solvers such as \texttt{PETSc} \citep{Preprint.Abhyankar}, \texttt{MUMPS} \citep{SIAM.01.Amestoy}, or \texttt{PARDISO} \citep{FGCS.04.Schenk}.}
\label{tbl:codecomparison}
  \begin{tabularx}{\linewidth}{lXXXX}
  \toprule
  %
  & \custem & \emg3d & \petgem & \simpeg  \\
  \midrule
  %
  Website & \href{https://custem.rtfd.io}{custem.rtfd.io}
          & \href{https://emsig.github.io}{emsig.github.io}
          & \href{http://petgem.bsc.es}{petgem.bsc.es}
          & \href{https://docs.simpeg.xyz}{simpeg.xyz} \\
  License & GPL-3.0 & Apache-2.0 & BSD-3-Clause & MIT \\
  Installation & \texttt{conda}
               & \texttt{pip}; \texttt{conda}
               & \texttt{pip}
               & \texttt{pip}; \texttt{conda} \\
  Comp. Dom. & frequency \& time & frequency & frequency & frequency \& time \\
  Method & FE & FV & FE & FV \\
  Mesh & tetrahedral & rectilinear & tetrahedral & recti-/curvilinear, octree \\
  BC & PEC; PMC & PEC & PEC & PEC; PMC \\
  Solver & \texttt{MUMPS} & \emg3d & \texttt{PETSc}; \texttt{MUMPS} &
           \texttt{PARDISO}; \texttt{MUMPS} \\
  %
  \bottomrule
\end{tabularx}
\end{minipage}
\end{table*}
%

@@

The full MR3D model consists of $1022\times371\times1229$ cells, totalling to almost 466 million cells, where each cell has dimensions of $25\times75\times5$\,m. The model was upscaled for the computation to $515\times563\times310$ cells, totalling to almost 90 million cells, where each cell has dimensions of $100\times100\times20$\,m. Both the full model and the upscaled computational model are released as open source. The published data set consists of a regular grid of receivers of 20 in eastern direction by 25 in northern direction, 500 receivers in total, with 1\,km spacing located on the irregular seafloor. 45 source-towlines were located on the same grid above each receiver line, 50\,m above the seafloor, with shots every 100\,m. The computed responses for one of the receivers, \texttt{04Rx251a}, are shown in the original publication for the East-West inline-source \texttt{04Tx013a} and the East-West broadside-source \texttt{04Tx014a} (broadside offset of 1\,km). We reproduce the responses for this receiver and corresponding source-lines in our comparison. The $x$-$z$ cross-section of the horizontal resistivity model at the receiver position is shown in Figure~\ref{fig:model-marlim}, together with the receiver and sources positions. All layer have a VTI with $\lambda=\sqrt{2}$, except for the air layer, the seawater, and the salt layer, which are all isotropic.

>>>>

\date{Accepted 2021 June 17. Received 2021 June 8; in original form 2020 October 23}
\pagerange{\pageref{firstpage}--\pageref{lastpage}}
% \volume{VVV}
\pubyear{2021}

@@

%
\begin{table*}
\begin{minipage}{.9\linewidth}
  \centering
  \caption{Comparison of the four codes under consideration. Note that \emg3d is a solver on its own, while the other codes implement third-package solvers such as \texttt{PETSc} \citep{Preprint.Abhyankar}, \texttt{MUMPS} \citep{SIAM.01.Amestoy}, or \texttt{PARDISO} \citep{FGCS.04.Schenk}.}
\label{tbl:codecomparison}
  \begin{tabularx}{\linewidth}{lXXXX}
  \toprule
  %
  & \custem & \emg3d & \petgem & \simpeg  \\
  \midrule
  %
  Website & \href{https://custem.rtfd.io}{custem.rtfd.io}
          & \href{https://emsig.xyz}{emsig.xyz}
          & \href{http://petgem.bsc.es}{petgem.bsc.es}
          & \href{https://docs.simpeg.xyz}{simpeg.xyz} \\
  License & GPL-3.0 & Apache-2.0 & BSD-3-Clause & MIT \\
  Installation & \texttt{conda}
               & \texttt{pip}; \texttt{conda}
               & \texttt{pip}
               & \texttt{pip}; \texttt{conda} \\
  Comp. Dom. & frequency \& time & frequency & frequency & frequency \& time \\
  Method & FE & FV & FE & FV \\
  Mesh & tetrahedral & rectilinear & tetrahedral & recti-/curvilinear, octree \\
  BC & PEC; PMC & PEC & PEC & PEC; PMC \\
  Solver & \texttt{MUMPS} & \emg3d & \texttt{PETSc}; \texttt{MUMPS} &
           \texttt{PARDISO}; \texttt{MUMPS} \\
  %
  \bottomrule
\end{tabularx}
\end{minipage}
\end{table*}
%

@@

The full MR3D model consists of $1022\times371\times1229$ cells, totalling to almost 466 million cells, where each cell has dimensions of $25\times75\times5$\,m. The model was upscaled for the computation to $515\times563\times310$ cells, totalling to almost 90 million cells, where each cell has dimensions of $100\times100\times20$\,m. Both the full model and the upscaled computational model are released openly. The published data set consists of a regular grid of receivers of 20 in eastern direction by 25 in northern direction, 500 receivers in total, with 1\,km spacing located on the irregular seafloor. 45 source-towlines were located on the same grid above each receiver line, 50\,m above the seafloor, with shots every 100\,m. The computed responses for one of the receivers, \texttt{04Rx251a}, are shown in the original publication for the East-West inline-source \texttt{04Tx013a} and the East-West broadside-source \texttt{04Tx014a} (broadside offset of 1\,km). We reproduce the responses for this receiver and corresponding source-lines in our comparison. The $x$-$z$ cross-section of the horizontal resistivity model at the receiver position is shown in Figure~\ref{fig:model-marlim}, together with the receiver and sources positions. All layer have a VTI with $\lambda=\sqrt{2}$, except for the air layer, the seawater, and the salt layer, which are all isotropic.
